DATA 621 - Business Analytics and Data Mining

### 2020-11-26 HW5/HW5-Draft.Rmd
ZI-Poisson 2 is best

## Selection

@@

# CODE APPENDIX
```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
<!-- Assignment -->
```{r loadData}
```
<!-- Data Exploration -->
```{r missingVal}
```
```{r statsN}
```
```{r graphsD}
```
```{r graphsH}
```
```{r corrgram}
```
```{r targetH}
```
<!-- Data Preparation -->
```{r trainTestSplit}
```
```{r model1addVars}
```
```{r model1impute}
```
```{r m1postImputeD}
```
```{r m1postImputeH}
```
```{r m2clean}
```
```{r model3impute}
```
<!-- Build Models -->
```{r m1PTrain}
```
```{r m1PTable}
```
```{r m1PFitCheck}
```
```{r m1PvarImp}
```
```{r m1NBTrain}
```
```{r m1NBTable}
```
```{r m1NBvarImp}
```
```{r m1PNB}
```
```{r m2poisson}
```
```{r m2PTable}
```
```{r m2PFitCheck}
```
```{r m1MLRFit}
```
```{r m1MLRTable}
```
```{r m2NBTrainBase}
```
```{r m2NBTrain}
```
```{r m2MLTrainBase}
```
```{r m2MLTrain}
```
<!-- Select Models -->
```{r compTable}
```
```{r m1TestProcess}
```
```{r m1PTest}
```
```{r m2TestProcess}
```
```{r m2PTest}
```
```{r m1NBTest}
```
```{r m2NBTest}
```
```{r m1MLRTest}
```
```{r m2MLTest}
```
<!-- Remaining Test sets go here -->
```{r modelTestResults}
```

>>>>

## Selection
The zero-inflated **Poisson Model 2** performed best on all the metrics and will
be used to create the prediction on the evaluation set.

@@

# CODE APPENDIX
```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
<!-- Assignment -->
```{r loadData}
```
<!-- Data Exploration -->
```{r missingVal}
```
```{r statsN}
```
```{r graphsD}
```
```{r graphsH}
```
```{r corrgram}
```
```{r targetH}
```
<!-- Data Preparation -->
```{r trainTestSplit}
```
```{r model1addVars}
```
```{r model1impute}
```
```{r m1postImputeD}
```
```{r m1postImputeH}
```
```{r m2clean}
```
```{r model3impute}
```
<!-- Build Models -->
```{r m1PTrain}
```
```{r m1PTable}
```
```{r m1PFitCheck}
```
```{r m1PvarImp}
```
```{r m1NBTrain}
```
```{r m1NBTable}
```
```{r m1NBvarImp}
```
```{r m1PNB}
```
```{r m2poisson}
```
```{r m2PTable}
```
```{r m2PFitCheck}
```
```{r m1MLRFit}
```
```{r m1MLRTable}
```
```{r m2NBTrainBase}
```
```{r m2NBTrain}
```
```{r m2MLTrainBase}
```
```{r m2MLTrain}
```
<!-- Select Models -->
```{r compTable}
```
```{r m1TestProcess}
```
```{r m1PTest}
```
```{r m2TestProcess}
```
```{r m2PTest}
```
```{r m1NBTest}
```
```{r m2NBTest}
```
```{r m1MLRTest}
```
```{r m2MLTest}
```
```{r modelTestResults}
```
